Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2023-02-26 Thesis/chapter/031-theory-calculations.tex
change from article to report

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Machine Learning and Statistics}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Why introduce machine learning to this project? 
%I wanted to apply and delve into what I've been studying during my undergrad courses. 
%This seemed like the perfect oppurtunity. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Is machine learning just hyped statistics? No! 
		%{https://doi.org/10.1177\%2F1352458520978648}
		%{Machine and deep learning in MS research are just powerful statistics – No}
What is \gls{ml}? Some might argue that \gls{ml} is just overglorified statistics, but that's not the case. 
Although \gls{ml} uses several statistical methods, their goal and frame conditions are different. 
%\td{The goal of machine learning is to ???}
%
\Gls{ml} tries to predict unseen data points and statistics is a subfield of maths 
which tries to get insight into a given data. 
For example, in a statistical model, it is desirable to reduce the number of inputs. 
This allows the statistician to better study how a change in the input variable can be 
directly affected by the output variable.\cite{gontcharov2019}
%pic from \url{https://towardsdatascience.com/notes-on-artificial-intelligence-ai-machine-learning-ml-and-deep-learning-dl-for-56e51a2071c2}
More precisely, mathematical statistics (stochastic)\cite{haertler2014statistisch} is the subject of 
finding mathematical models to describe the data 
whereas (classical) statistics is the domain of representing the data.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Artificial Inteligence and Machine Learning}
%How can \gls{ai} and \gls{ml} be defined? 
\Gls{ai} is a trans-disciplinary field with roots in logic, statistics, cognitive psychology, decision theory, neuroscience, linguistics, cybernetics, and computer engineering\cite{howard2019artificial}.
The history of \gls{ai} goes back to the middle of the \nth{20} century. 
Researchers from the emerging field came together at the Dartmouth conference and the term "\gls{ai}" was coined\cite{McCarthy1955}. 
\Gls{ai}'s  history is beautifully depicted by McCorducks' 1982 book "Machines Who Think"\cite{McCorduck1982,Apter1982}, which focuses on the great minds behind the advances.
Pioneers like Alan Turing thought a lot about how to define, test and implement \gls{ai}\cite{howard2019artificial}. 
One example how to measure \gls{ai} is to let it play chess against a human\cite{Silver2017} 
(in 1997 a chess computer called Deep Blue won against the World Chess Champion Garry Kasparov for the first time\cite{Feng1999}).
Another test \textit{ingenioused} by Alan Turing, is the imitation game\cite{turing1950imitation}, nowadays known as Turing test.
An interrogator communicates with two unknown entities \textbf{A} and \textbf{B} (a woman and a man) and must find out who is who. 
\textbf{A} will try to make to interrogator misjudge, whereas \textbf{B} is on the interrogators side.
The question is if \textbf{A} is replaced with a computer how the ratio of outcomes would deviate from the original ratio. 
%
At the moment it's hard to imagine a computer getting a higher ratio than a human
but when reading AI written articles\cite{gpt2020}, it's easy to see this test being passed in the future.

@@

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Machine Learning Methods}
%
\Gls{ml} is at the base of most \gls{ai}s.
It is an umbrella term for programs with instructions to learn from data, i.e. gain knowledge, categorise, predict and make decisions based on data. 
%
There is a platitude of different machine learning methods: 
they can be divided into supervised (training set is labeled) and unsupervised (exploratory).  
An orthogonal division can be made by regression (continuous data) versus classification (discrete, categorical data). 
Independent from these $2\times2$ categories there are multiple ways to let machines learn from data.
%
\Gls{nn} (one of the most popular architectures for big data\cite{Chiroma2019}) are loosely modeled after the brain\cite{bishop1994neural}.
Artificial neurons (also called nodes), which are arranged in layers, 
are connected to each of the neurons of previous and next layers
and the weights (parameters of intensity), with which the data is routed from one neuron to another, 
are optimised during training. 
%
Convolutional-layer \gls{nn} excel in picture recognition\cite{Lecun1995conv} and are useful in quantum mechanics too\cite{westermayr2020combining}.
Other common architectures include linear regression, kernel ridge regression and support vector regression.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Population Based Optimisation Algorithms}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{EMMA}
\Gls{emma} is an implementation of the \gls{pso} in the \texttt{R} programming language. 
Each time step the dependent variables for all possible input variable combinations %$\mathbf{x} = \{x_1,\cdots ,x_N\}$ 
are predicted with the help of \gls{mars}. 
The \gls{mars} \gls{rf} is then used to chose the next position for each particle.
\Gls{mars} is a regression method introduced by Friedman's 1991 paper 
"Multivariate Adaptive Regression Splines"\cite{friedman1991multivariate}. 
The \texttt{CRAN} package which implements \gls{mars} is called \texttt{earth} due to \gls{mars} being trade marked\cite{mars}.
%%% MARS 
\gls{mars} is an extension of multivariate linear regression.
Friedman presented \gls{mars} as an alternative to piecewise polynomials (splines) and local averaging methods (e.g. kernel functions), whose number of parameter quickly exceeds the practical for moderate dimensional problems ($n>5$). 
%
%to higher dimensions (n > 2) is straightforward in principle but difficult in practice. 
%"These difficulties are related to the so-called “curse-of-dimensionality”, a phrase coined by Bellman (1961) to express the fact that exponentially increasing numbers of points are needed to densely populate Euclidean spaces of increasing dimension."\cite{friedman1988fitting}
%
The main advancements of \gls{mars} are the ability to fit (possibly complex) interactions and non-linearities without losing interpretability. 
%
%- "The key ingredient that advances this approach to general settings is the ability to fit (possibly complex) interactions among the variables through the product terms that are permitted to enter the approximation (9), if required by the fit."\cite{friedman1988fitting}
%% MARS MODEL SELECTION
%- "The approximation is developed in a forward/backwards stepwise recursive manner in analogy with the recursive partitioning approach. "\cite{friedman1988fitting}
%
%%% FORWARD MARS
The \gls{rf} is developed in a forward/backward stepwise recursive manner\cite{friedman1988fitting}. 
During the forward recursion terms are added in pairs until a certain number of terms is reached. 
Each pair consists of two hinge functions (also called rectifier functions) multiplied with a term already part of the \gls{rf} (including the constant term).
The maximum degree of interaction is 2 for \gls{emma}, but can be varied. 
This means that only two basis functions can be multiplied (excluding the constant term) to form a subsequent term.
Pairwise added hinge functions are of the simple form $h(x-c)$ and $h(c-x)$ where $h(a)= max(0,a)$ and with $x$ being an independent variable, $c$ being a constant and $a$ being any expression. 
%%% BACKWARD EMMA
Then, the backwards algorithm regularizes the function by removing individual terms. 
The metric which decides if a term should be removed is called \gls{gcv} and was introduced by Wahba and Cravenin 1969\cite{wahba1979smoothing}.

@@

\iffalse
\subsubsection{Kernel Ridge Regression and Support Vector Machine}
\textbf{goal}
\begin{itemize}
    \item intro to stat and ml 
    \item say that although different will be abgehandelt in the same chapter 
    \item basic statistics: MAE vs MSE, R, std, F-test 
    \item lin reg 
    \item ridge regression 
    \item kernel ridge regression 
    \item support vector machine 
    \item anova (categorical), PCA, step wise regression
    \item all previous ananlyse data to predict, but don't tell me which data point is needed next 
    \item DOE (add data acquisition)
    \item genetic algorithm and pso (they combine data gen with regression/prediction and optimisation, actually incorporate prediction into selection process but don't per se specify which pred and optimisation)
    \item comment: always tradeoff between complexity and interpretability
    \item quesiton: which paragraph by GPT2?? 
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%% STATISTICS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Design of Experiment} %DOE
%\epigraph{"The real purpose of experiment design is to maximize the information content of the data within the limits imposed by the given constraints."}{Grahem C. Goodwin\cite{goodwin1977experiment}}
%"Our ability to design a good experiment should depend upon our prior knowledge regarding the nature of the data generating mechanism."\cite{goodwin1977experiment}
%
\begin{quote}
	{"The real purpose of experiment design is to maximize the information content of the data within the limits imposed by the given constraints."}
	- {Grahem C. Goodwin\cite{goodwin1977experiment}}
\end{quote}
%
In two cases a deliberate \gls{doe} is beneficial.
If the query of a new data point is very expensive, it is favourable to actively chose the query (e.g. drilling for oil or quantum chemical calculations). 
If the query space is so vast, that randomly querying might explore domains which might lead to uninteresting or even misleading information.
%Both encompass nearly all cases. 
% 
At the beginning of any experiment its constraints must be determined. 
%
Constraints for a given experiment include range of input and output variables as well as total time available and total number of samples/experiments that can be taken.\cite{goodwin1977experiment}
%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Analysis of Variance} % ANOVA
\Gls{anova} is a statistical test for estimating the influence of multiple categorical independent variables on a dependent numerical variable. 
At the heart of \gls{anova} lies the F-test. 
The F-test was \textit{ingeniused} by Ronald Fisher\cite{fisher1921on}, an important figure in modern statistics. 
The F-test uses a ratio of variances to determine if a null-hypothesis (observed difference is due to chance alone) is true. 
The variance in the enumerator measures the "between-group variability" and the denominator measures the "within-group variability".
This ratio is unaffected by units, scaling errors and constant bias. 
%
Additional assumptions of \gls{anova} include: groups and levels should be independent, 
residual error should follow normal distribution and variance within groups should be equal (homoscedasticity). 
%\Gls{anova} analyses the means by means of mincing variances.
%of of the continuous outputs where inputs are categories. 
%The statistical significance of the experiment is determined by a ratio of two variances. 
%This ratio is independent of several possible alterations to the experimental observations: 
%Adding a constant to all observations does not alter significance. 
%Multiplying all observations by a constant does not alter significance. 
%\Gls{anova} statistical significance results are independent of constant bias and 
%scaling errors as well as the units used in expressing observations. 
%\href{https://en.wikipedia.org/wiki/Analysis_of_variance#Summary_of_assumptions}{(click here)}
%\href{https://statsandr.com/blog/anova-in-r/}{(click here)}

@@

%%% FEATURE SELECTION 
% https://stats.stackexchange.com/questions/39243/how-does-one-interpret-svm-feature-weights
% gene (feature) selection with SVM https://link.springer.com/content/pdf/10.1023/A:1012487302797.pdf
% Intro to feature selection https://axon.cs.byu.edu/Dan/778/papers/Feature%20Selection/guyon2.pdf
\iffalse
%%% VALIDATION 
\subsubsection{Validation}
Validation is an important part of data analysis as it allows to estimate model errors. 
Often used methods are analysis of residual error, cross validation and leave-one-out validation\cite{kartam1997artificial}.
\td{to do read kartam}
statistical methods to bewerten a model are: 
cross validation, leave-one-out validation ( special case of cross validation), correlation coefficient for linear fits, mean square error, mean absolute erro
\td{cite from Hawkins 2004\cite{hawkins2004overfitting}}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Machine Learning and Statistics}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Why introduce machine learning to this project? 
%I wanted to apply and delve into what I've been studying during my undergrad courses. 
%This seemed like the perfect oppurtunity. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Is machine learning just hyped statistics? No! 
		%{https://doi.org/10.1177\%2F1352458520978648}
		%{Machine and deep learning in MS research are just powerful statistics – No}
What is \gls{ml}? Some might argue that \gls{ml} is just overglorified statistics, but that's not the case. 
Although \gls{ml} uses several statistical methods, their goal and frame conditions are different. 
%\td{The goal of machine learning is to ???}
%
\Gls{ml} tries to predict unseen data points and statistics is a subfield of maths 
which tries to get insight into a given data. 
For example, in a statistical model, it is desirable to reduce the number of inputs. 
This allows the statistician to better study how a change in the input variable can be 
directly affected by the output variable.\cite{gontcharov2019}
%pic from \url{https://towardsdatascience.com/notes-on-artificial-intelligence-ai-machine-learning-ml-and-deep-learning-dl-for-56e51a2071c2}
More precisely, mathematical statistics (stochastic)\cite{haertler2014statistisch} is the subject of 
finding mathematical models to describe the data 
whereas (classical) statistics is the domain of representing the data.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Artificial Inteligence and Machine Learning}
%How can \gls{ai} and \gls{ml} be defined? 
\Gls{ai} is a trans-disciplinary field with roots in logic, statistics, cognitive psychology, decision theory, neuroscience, linguistics, cybernetics, and computer engineering\cite{howard2019artificial}.
The history of \gls{ai} goes back to the middle of the \nth{20} century. 
Researchers from the emerging field came together at the Dartmouth conference and the term "\gls{ai}" was coined\cite{McCarthy1955}. 
\Gls{ai}'s  history is beautifully depicted by McCorducks' 1982 book "Machines Who Think"\cite{McCorduck1982,Apter1982}, which focuses on the great minds behind the advances.
Pioneers like Alan Turing thought a lot about how to define, test and implement \gls{ai}\cite{howard2019artificial}. 
One example how to measure \gls{ai} is to let it play chess against a human\cite{Silver2017} 
(in 1997 a chess computer called Deep Blue won against the World Chess Champion Garry Kasparov for the first time\cite{Feng1999}).
Another test \textit{ingenioused} by Alan Turing, is the imitation game\cite{turing1950imitation}, nowadays known as Turing test.
An interrogator communicates with two unknown entities \textbf{A} and \textbf{B} (a woman and a man) and must find out who is who. 
\textbf{A} will try to make to interrogator misjudge, whereas \textbf{B} is on the interrogators side.
The question is if \textbf{A} is replaced with a computer how the ratio of outcomes would deviate from the original ratio. 
%
At the moment it's hard to imagine a computer getting a higher ratio than a human
but when reading AI written articles\cite{gpt2020}, it's easy to see this test being passed in the future.

@@

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Machine Learning Methods}
%
\Gls{ml} is at the base of most \gls{ai}s.
It is an umbrella term for programs with instructions to learn from data, i.e. gain knowledge, categorise, predict and make decisions based on data. 
%
There is a platitude of different machine learning methods: 
they can be divided into supervised (training set is labeled) and unsupervised (exploratory).  
An orthogonal division can be made by regression (continuous data) versus classification (discrete, categorical data). 
Independent from these $2\times2$ categories there are multiple ways to let machines learn from data.
%
\Gls{nn} (one of the most popular architectures for big data\cite{Chiroma2019}) are loosely modeled after the brain\cite{bishop1994neural}.
Artificial neurons (also called nodes), which are arranged in layers, 
are connected to each of the neurons of previous and next layers
and the weights (parameters of intensity), with which the data is routed from one neuron to another, 
are optimised during training. 
%
Convolutional-layer \gls{nn} excel in picture recognition\cite{Lecun1995conv} and are useful in quantum mechanics too\cite{westermayr2020combining}.
Other common architectures include linear regression, kernel ridge regression and support vector regression.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Population Based Optimisation Algorithms}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{EMMA}
\Gls{emma} is an implementation of the \gls{pso} in the \texttt{R} programming language. 
Each time step the dependent variables for all possible input variable combinations %$\mathbf{x} = \{x_1,\cdots ,x_N\}$ 
are predicted with the help of \gls{mars}. 
The \gls{mars} \gls{rf} is then used to chose the next position for each particle.
\Gls{mars} is a regression method introduced by Friedman's 1991 paper 
"Multivariate Adaptive Regression Splines"\cite{friedman1991multivariate}. 
The \texttt{CRAN} package which implements \gls{mars} is called \texttt{earth} due to \gls{mars} being trade marked\cite{mars}.
%%% MARS 
\gls{mars} is an extension of multivariate linear regression.
Friedman presented \gls{mars} as an alternative to piecewise polynomials (splines) and local averaging methods (e.g. kernel functions), whose number of parameter quickly exceeds the practical for moderate dimensional problems ($n>5$). 
%
%to higher dimensions (n > 2) is straightforward in principle but difficult in practice. 
%"These difficulties are related to the so-called “curse-of-dimensionality”, a phrase coined by Bellman (1961) to express the fact that exponentially increasing numbers of points are needed to densely populate Euclidean spaces of increasing dimension."\cite{friedman1988fitting}
%
The main advancements of \gls{mars} are the ability to fit (possibly complex) interactions and non-linearities without losing interpretability. 
%
%- "The key ingredient that advances this approach to general settings is the ability to fit (possibly complex) interactions among the variables through the product terms that are permitted to enter the approximation (9), if required by the fit."\cite{friedman1988fitting}
%% MARS MODEL SELECTION
%- "The approximation is developed in a forward/backwards stepwise recursive manner in analogy with the recursive partitioning approach. "\cite{friedman1988fitting}
%
%%% FORWARD MARS
The \gls{rf} is developed in a forward/backward stepwise recursive manner\cite{friedman1988fitting}. 
During the forward recursion terms are added in pairs until a certain number of terms is reached. 
Each pair consists of two hinge functions (also called rectifier functions) multiplied with a term already part of the \gls{rf} (including the constant term).
The maximum degree of interaction is 2 for \gls{emma}, but can be varied. 
This means that only two basis functions can be multiplied (excluding the constant term) to form a subsequent term.
Pairwise added hinge functions are of the simple form $h(x-c)$ and $h(c-x)$ where $h(a)= max(0,a)$ and with $x$ being an independent variable, $c$ being a constant and $a$ being any expression. 
%%% BACKWARD EMMA
Then, the backwards algorithm regularizes the function by removing individual terms. 
The metric which decides if a term should be removed is called \gls{gcv} and was introduced by Wahba and Cravenin 1969\cite{wahba1979smoothing}.

@@

\iffalse
\subsection{Kernel Ridge Regression and Support Vector Machine}
\textbf{goal}
\begin{itemize}
    \item intro to stat and ml 
    \item say that although different will be abgehandelt in the same chapter 
    \item basic statistics: MAE vs MSE, R, std, F-test 
    \item lin reg 
    \item ridge regression 
    \item kernel ridge regression 
    \item support vector machine 
    \item anova (categorical), PCA, step wise regression
    \item all previous ananlyse data to predict, but don't tell me which data point is needed next 
    \item DOE (add data acquisition)
    \item genetic algorithm and pso (they combine data gen with regression/prediction and optimisation, actually incorporate prediction into selection process but don't per se specify which pred and optimisation)
    \item comment: always tradeoff between complexity and interpretability
    \item quesiton: which paragraph by GPT2?? 
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%% STATISTICS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Design of Experiment} %DOE
%\epigraph{"The real purpose of experiment design is to maximize the information content of the data within the limits imposed by the given constraints."}{Grahem C. Goodwin\cite{goodwin1977experiment}}
%"Our ability to design a good experiment should depend upon our prior knowledge regarding the nature of the data generating mechanism."\cite{goodwin1977experiment}
%
\begin{quote}
	{"The real purpose of experiment design is to maximize the information content of the data within the limits imposed by the given constraints."}
	- {Grahem C. Goodwin\cite{goodwin1977experiment}}
\end{quote}
%
In two cases a deliberate \gls{doe} is beneficial.
If the query of a new data point is very expensive, it is favourable to actively chose the query (e.g. drilling for oil or quantum chemical calculations). 
If the query space is so vast, that randomly querying might explore domains which might lead to uninteresting or even misleading information.
%Both encompass nearly all cases. 
% 
At the beginning of any experiment its constraints must be determined. 
%
Constraints for a given experiment include range of input and output variables as well as total time available and total number of samples/experiments that can be taken.\cite{goodwin1977experiment}
%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Analysis of Variance} % ANOVA
\Gls{anova} is a statistical test for estimating the influence of multiple categorical independent variables on a dependent numerical variable. 
At the heart of \gls{anova} lies the F-test. 
The F-test was \textit{ingeniused} by Ronald Fisher\cite{fisher1921on}, an important figure in modern statistics. 
The F-test uses a ratio of variances to determine if a null-hypothesis (observed difference is due to chance alone) is true. 
The variance in the enumerator measures the "between-group variability" and the denominator measures the "within-group variability".
This ratio is unaffected by units, scaling errors and constant bias. 
%
Additional assumptions of \gls{anova} include: groups and levels should be independent, 
residual error should follow normal distribution and variance within groups should be equal (homoscedasticity). 
%\Gls{anova} analyses the means by means of mincing variances.
%of of the continuous outputs where inputs are categories. 
%The statistical significance of the experiment is determined by a ratio of two variances. 
%This ratio is independent of several possible alterations to the experimental observations: 
%Adding a constant to all observations does not alter significance. 
%Multiplying all observations by a constant does not alter significance. 
%\Gls{anova} statistical significance results are independent of constant bias and 
%scaling errors as well as the units used in expressing observations. 
%\href{https://en.wikipedia.org/wiki/Analysis_of_variance#Summary_of_assumptions}{(click here)}
%\href{https://statsandr.com/blog/anova-in-r/}{(click here)}

@@

%%% FEATURE SELECTION 
% https://stats.stackexchange.com/questions/39243/how-does-one-interpret-svm-feature-weights
% gene (feature) selection with SVM https://link.springer.com/content/pdf/10.1023/A:1012487302797.pdf
% Intro to feature selection https://axon.cs.byu.edu/Dan/778/papers/Feature%20Selection/guyon2.pdf
\iffalse
%%% VALIDATION 
\subsection{Validation}
Validation is an important part of data analysis as it allows to estimate model errors. 
Often used methods are analysis of residual error, cross validation and leave-one-out validation\cite{kartam1997artificial}.
\td{to do read kartam}
statistical methods to bewerten a model are: 
cross validation, leave-one-out validation ( special case of cross validation), correlation coefficient for linear fits, mean square error, mean absolute erro
\td{cite from Hawkins 2004\cite{hawkins2004overfitting}}
